% ---------------------------------
% -- Assignment 1: Chapter 1, #1 --
% -- Math 4141 --------------------

% Set document type
\documentclass[11pt,oneside]{extarticle}


\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{thmtools}
\usepackage{fontspec}
\usepackage[margin=0.5in]{geometry}
\usepackage{inputenc}
%\usepackage{unicode-math}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{garamondx}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{listings}
\usepackage{newtxmath}
\usepackage{solarized-light}
\usepackage{xcolor}
%\usepackage{lmodern}

%\usepackage[default]{sourcecodepro}
\usepackage[T1]{fontenc}
%\usepackage{inconsolata}
% Real number symbol
\newcommand{\Real}{\mathbb{R}}
\newcommand{\dprime}{{\prime\prime}}
%\newcommand{\min}{\mathrm{min}\:}

% Set typewriter font to Source Code Pro
%\renewcommand{\ttfamily}{\tiny\sourcecodepro}

% Change enumerator to use letters i.e., a, b, c, ...
\renewcommand{\theenumi}{\alph{enumi}}

\setlength{\belowcaptionskip}{-12pt}
%\setttfont{

\begin{document}
\section{Golden Method}

\begin{enumerate}
    
    \item Consider the Golden method for $\min g(x)$ in $[a,b]$. Prove that
        $1/R = (\sqrt{5} - 1) / 2$.

    \item Use the Golden Method to find the minimum point of function

        $$g(x) = 3\sin x\cos x + 2$$
        in $[a_1,b_1]=[1.5,3.2]$ with $k=4$ (stop at $k=4$).

    \item Explain two advantages of the Golden Method over a search method
        with $\rho=2/3$.

\end{enumerate}

\section{Fibonacci Method}

\begin{enumerate}

    \item Consider the Fibonacci method for solving $\min g(x)$ in $[a,b]$.
        Prove that

        $$\frac{I_n}{I_{n-k}}=\frac{1}{F_{k+1}}, k=1,\ldots,n-1$$

        $$\frac{I_k}{I_1}=\frac{F_{n-k+1}}{F_n}, k=2,3,\ldots,n,$$

        where $F_j,j>0$ are the Fibonacci numbers.

    \item Let stop be at $n=9$ in the Fibonacci method. Find $I_2/I_1,I_4/I_1,
        I_8/I_1$.

\end{enumerate}

\section{Simplex Method}

    \begin{enumerate}

        \item In the Simplex method, give the formulas of locations of
            $a^\prime, a^\dprime, a^*, a^{**}, \bar{a},$ and $\bar{b}$.

        \item Consider the minimization function

            $$g(x,y) = 2x^2 - x - 2y + y^2 + 4.$$

            Starting from the initial triangle $\Delta a_0b_0c_0$, where
            $a_0(0.1,0), b_0(0.0,0.1), c_0(0.0,0.0)$, do two steps (i.e. find
            $\Delta a_2,b_2,c_2$ ) by the simplex method. What is your approximation
            to the minimum point? What are the advantages and drawbacks of the
            simplex method?

    \end{enumerate}

\section{Steepest Descent Method}

Consider the Steepest Descent method for solving the local minimization of
$\min g(\vec{x})$ in $\Omega\subset\Real^n$.

    \begin{enumerate}

        \item If the previous approximation is $\vec{x}^{(k-1)}$, what is the
            $k$'th step search direction $\vec{z}^{(k)}$? Explain briefly why
            you use this search direction.

        \item Write out the Algorithm of the Steepest Descent Method. You need
            to provide the following details:

    \end{enumerate}

\section{Application}

Let

$$g(x,y) = -\left( x^2 + 4xy + 2y^2 \right) e^{ -2x^2 - y^2 }.$$

Use a computer to approximate the local minimization problem of $\min g(x,y)$
in $\Real^2$ by \emph{one} of the numerical methods: Newton's method, the Steepest
Descent method, or the simplex method.

\begin{enumerate}

    \item Explain briefly how to solve the problem by the method that you used.

    \item Set up a table of numerical results and iteration numbers by using
        initial guesses and tolerances. Analyze your results.

    \item What are the advantages and drawbacks of the method based on your
        analysis?

\end{enumerate}





\end{document}
